Hierarchical Dispatching and Overriding

### 2017-10-09 NewVersion/sections/Introduction.tex
S1

C++ and C\# do allow for two
unintentionally conflicting methods to coexist in a class. 
C++ accepts the triangle inheritance and
resolves the ambiguity by \emph{static dispatching} or casts. But the
drawback is that these conflicting methods cannot be further overriden. 
\bruno{how about C\#? Say something about C\# here.}
% However, C++ has
% limited support for virtual methods with unintentional conflicts, and
% it will often throw errors when composing them. This is again
% unsatisfactory because virtual methods are pervasive in OOP and used 
% for code reuse and extensibility. A problem with the C++ approach is
% that programmers can only use either static or dynamic dispatching separately, but dealing
% with unintentional method conflicts seems to require a combination of
% both. 
Some other workarounds or approaches include delegation and
renaming/exclusion in the trait model. However renaming/exclusion 
can break the subtyping relation between a subclass and its parent.
This is not adequate for the class model commonly used in mainstream 
OOP languages, where the subclass is always expected to be a subtype 
of the parent class.

>>>>

C++ and C\# do allow for two
unintentionally conflicting methods to coexist in a class. C\# allows this by interface multiple inheritance and explicit method implementation, but there are people argue that in C\# you cannot do "multiple inheritance" \emph{from} interfaces, you can only \emph{implement} multiple interfaces. We will have more detailed discussion on this in Section~\ref{sec:relatedwork}.
C++ accepts the triangle inheritance and
resolves the ambiguity by specifying the expected path by \emph{upcasts}. But the
drawback is that these conflicting methods cannot be further overriden. 
\bruno{how about C\#? Say something about C\# here.}\yanlin{added C\#}
% However, C++ has
% limited support for virtual methods with unintentional conflicts, and
% it will often throw errors when composing them. This is again
% unsatisfactory because virtual methods are pervasive in OOP and used 
% for code reuse and extensibility. A problem with the C++ approach is
% that programmers can only use either static or dynamic dispatching separately, but dealing
% with unintentional method conflicts seems to require a combination of
% both. 
Some other workarounds or approaches include delegation and
renaming/exclusion in the trait model. However renaming/exclusion 
can break the subtyping relation between a subclass and its parent.
This is not adequate for the class model commonly used in mainstream 
OOP languages, where the subclass is always expected to be a subtype 
of the parent class.
